#pip install virtualenv
#py -m venv venv
#.\venv\Scripts\Activate
#pip install django
#django-admin startproject quiz_game . = el punto es para que lo cree en la raiz de la app
#python manage.py runserver
#python manage.py startapp game

-- Crea en el folder que creaste un archivo urls.py i dentro crea las rutas globales 

from django.urls import path
from . import views
urlpatterns = [
    path('', views.hello),# el  '' esta vacio para que sea la primera vista 
    path('about/', views.about),# el  '' esta vacio para que sea la primera vista 
]

#python manage.py migrate

-- para ver las tables usa db broser 
#python manage.py makemigrations game  -- para crear la migraciones . rmb add the 'game' in settigs INSTALLED_APPS
#python manage.py migrate game  









4. What is the correct syntax to create a function in JavaScript?
Options:
function = myFunction()
function myFunction() {}
def myFunction()
func myFunction()
Correct Answer: function myFunction() {}
5. What is the output of 2 + "2" in JavaScript?
Options:
4
22
NaN
undefined
Correct Answer: 22
6. How do you add a comment in JavaScript?
Options:
<!-- This is a comment -->
// This is a comment
# This is a comment
* This is a comment *
Correct Answer: // This is a comment
7. What does isNaN() check for in JavaScript?
Options:
If a value is null
If a value is a number
If a value is not a number
If a value is undefined
Correct Answer: If a value is not a number
8. Which of the following is NOT a JavaScript data type?
Options:
String
Number
Boolean
Character
Correct Answer: Character
9. How do you call a function named myFunction in JavaScript?
Options:
call myFunction()
execute myFunction()
myFunction()
run myFunction()
Correct Answer: myFunction()
10. How do you round the number 4.7 down to the nearest whole number?
Options:
Math.round(4.7)
Math.floor(4.7)
Math.ceil(4.7)
Math.min(4.7)
Correct Answer: Math.floor(4.7)
